A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-06-02 04_Severity_MetaAnalysis.Rmd
add sensittivity analysis and I^2 heterogenety test

>>>>

```{r Sensitivity_logitP, cache=TRUE}
s_analysis <- 
   lapply(unique(PM_dat_D$trial_ref), function(Trial) {

      dat <- filter(PM_dat_D, trial_ref != Trial)
      # remove controls for response ratio meta-analysis
      rma.mv(
         yi = yi_logit,
         V = yi_logit,
         mods = ~ spray_management,
         method = "ML",
         random = list(~ spray_management | trial, ~ 1 | id),
         struct = "UN",
         control = list(optimizer = "optim"),
         data = dat
      )

   })

length(s_analysis)
est <- lapply(s_analysis, function(e1){
   data.frame(treat = rownames(e1$b),
              estimates = e1$b,
              p = as.numeric(reportP(e1$pval, P_prefix = FALSE,AsNumeric = TRUE)))
   })

sensitiviy_df <- data.table::rbindlist(est)
sensitiviy_df$Tnum <- rep(1:14, each = 6)

sensitiviy_df %>%
   ggplot(aes(Tnum, estimates, colour = treat))+
   geom_line()

sensitiviy_df %>%
   ggplot(aes(Tnum, p, colour = treat))+
   geom_line()

unique(PM_dat_D$trial_ref)[7]
sensitiviy_df %>%
   group_by(treat) %>%
   summarise(minEst = min(estimates),
             medEst = median(estimates),
             maxEst = max(estimates),
             minP = min(p),
             medP = median(p),
             maxP= max(p))
```
While estimates and P values remained the mostly same when each trial was dropped from the analysis. Estimates changed the most when Trial 1617/02 at Missen Flats in 2017 was ommited from the analysis.

Calculation of I^2
```{r}
W <- diag(1/(PM_dat_D$vi_logit+0.0001))
X <- model.matrix(PMsev_mvPer)
P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
100 * sum(PMsev_mvPer$sigma2) / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))

100 * PMsev_mvPer$sigma2 / (sum(PMsev_mvPer$sigma2) + (PMsev_mvPer$k-PMsev_mvPer$p)/sum(diag(P)))
```
This indicates that approximate amount of total variance attributed to trials/ clusters is 99%, which is very high. 
However given that many of the means included in the model contained an accompanying sample variance of zero, this might have been expected.
